The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2020-02-26 Paper/jaccardbaetica.tex
update wrong map

Stamps are the most studied in this type of amphorae. The fascination aroused by stamps has caused it to be one of the inscriptions with the most publications about its origin and meaning. Its endure in time become it an essential element that were used to mark amphorae during almost three centuries \citep{remesal_sellar_2016}. (Fig.\ref{amphora}).

@@

\xavi{veo cierta confusión de secciones...si todo esto hasta ahora es intro, entonces deberían ser subsecciones?}

\xavi{en todo caso debe quedar mucho más claro el objetivo del paper}

@@

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/dendroger5.pdf}
\caption{Dendrogram obtained by Morisita-Horn algorthm of different sites in Germania. Colours are represented by types of sites divided into military sites (red), civil sites (green) and no specific (grey)}
\label{germap}
\end{figure}

The sites with more similarity in stamps were closely located in limes. In this case, most sites have different stamps  which means that we did not detect any pattern. On the other hand, there seems to be a greater concentration of the seals in areas eminently militarized and close to the german limes. However, It is still no possible to determine with the data that the existence of a defined pattern that reflects in more detail the route of this production in the area of the German limes.

@@

%soltar aquí las hipótesis repito aquí several reasons no repetir

@@

\section{Acknowledgements}
%completar 
The research was funded by European Research Council Advanced Grant EPNet (340828). We are grateful to Simon Carrignon, Juan Moros and Ignacio Morer for their useful suggestions.  
All data has been analysed and conducted in R program version 3.2.4, using the packages \textit{vegan} \citep{oksanen_vegan_2007}, \textit{ggplot2} \citep{ggplot2:_2016}. Source and code are available

>>>>

Stamps are the most studied in this type of amphorae. The fascination aroused by stamps has caused it to be one of the inscriptions with the most publications about its origin and meaning. Its endure in time become it an essential element that were used to mark amphorae during almost three centuries \citep{remesal_sellar_2016} (Fig.\ref{amphora}).

@@

@@

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/dendroger5.pdf}
\caption{Dendrogram obtained by Morisita-Horn algorithm of different sites in Germania. Colours are represented by types of sites divided into military sites (red), civil sites (green) and no specific (grey)}
\label{germap}
\end{figure}

The sites with more similarity in stamps were closely located in limes. In this case, most sites have different stamps  which means that we did not detect any pattern. On the other hand, there seems to be a greater concentration of the seals in areas eminently militarized and close to the German limes. However, It is still no possible to determine with the data that the existence of a defined pattern that reflects in more detail the route of this production in the area of the German limes.

@@

@@

\section{Acknowledgements}
%completar 
The research was funded by European Research Council Advanced Grant EPNet (340828). We are grateful to Simon Carrignon, Juan Moros and Ignacio Morer for their useful suggestions.  
All data has been analysed and conducted in R program version 3.2.4, using the packages \textit{vegan} \citep{oksanen_vegan_2007}, \textit{ggplot2} \citep{ggplot2:_2016}. Source and code are available at \maria{incluir github}.
